Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-08-29 public/paper/pyg4ometry.tex
GDML to Fluka conversion figure

The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
producing an abstract syntax tree (AST).  The resulting AST is then
walked to populate Region instances with zones and bodies.  An example
FLUKA region with the corresponding abstract syntax tree is shown in
Figure~\ref{fig:region-ast}.
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML, a) 
the original FLUKA geometry displayed in FLAIR, b) the GDML geometry 
viewed in pyg4ometry. The example is a Faraday cup used to capture 
and measure accelerator beam charge}
\label{fig:region-ast}
\end{center}
\end{figure*}

@@

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
\caption{CAD-GDML}
\label{fig:cad-gdml}
\end{center}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
\caption{CAD-GDML}
\label{fig:model}
\end{center}
\end{figure*}

>>>>

The FLUKA CSG ASCII format is parsed using an ANTLR4-generated parser,
producing an abstract syntax tree (AST).  The resulting AST is then
walked to populate Region instances with zones and bodies.  An example
FLUKA region with the corresponding abstract syntax tree is shown in
Figure~\ref{fig:region-ast}.
\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/faradayCup2.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
the original FLUKA geometry displayed in FLAIR, right panel : the GDML geometry 
viewed in pyg4ometry. The example is a Faraday cup used to capture 
and measure accelerator beam charge.}
\label{fig:region-ast}
\end{center}
\end{figure*}

\begin{lstlisting}[caption={A simple pyg4ometry python script to load a FLUKA file},label={lst:pythonFLUKALoading}, language=Python]
    reader_faraday  = pyg4ometry.fluka.Reader("faradayCup2.inp")
    faraday_greg    = pyg4ometry.convert.fluka2Geant4(reader_faraday.flukaregistry)
    faraday_logical = faraday_greg.getWorldVolume()
    faraday_assembly = faraday_logical.assemblyVolume()
\end{lstlisting}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/CuboidalChamber.pdf}
\caption{Example conversion of a simple GDML geometry to FLUKA, left panel :  
the original model in pyg4ometry, right panel : the converted FLUKA geometry 
viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
\label{fig:flair-gdml}
\end{center}
\end{figure*}

@@

\begin{lstlisting}[caption={A simple pyg4ometry python script to load a STEP file},label={lst:pythonCADLoading}, language=Python]
    reader_dipole = pyg4ometry.freecad.Reader("./10_SectorBendMedium.step")
    reader_dipole.relabelModel()
    reader_dipole.convertFlat()
    dipole_reg = reader_dipole.getRegistry()
\end{lstlisting}

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/SectorBend.pdf}
\caption{Example conversion of a simple FLUKA geometry to GDML, left panel :  
the original model in FreeCAD, right panel : the GDML geometry 
viewed in pyg4ometry. The example is a sector bend dipole electromagnet.}
\label{fig:cad-gdml}
\end{center}
\end{figure*}

@@

\begin{figure*}[htbp]
\begin{center}
\includegraphics[width=1.0\textwidth]{./model-scene/model.pdf}
\caption{Complete compositing example using pyg4ometry.}
\label{fig:model}
\end{center}
\end{figure*}
